Expressive, Modular and Compositional Embedded DSLs

### 2015-05-20 dAlg/mrm.tex
Introduction
Revised Section 2
Format & small changes
JFP format

\documentclass[nocopyrightspace]{sigplanconf}

@@

\usepackage{xcolor}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\graphicspath{ {images/} }

@@

\newcommand\SM[1]{\textcolor{red!70!yellow}{[SM: #1]}}
\newcommand\BO[1]{\textcolor{green!70!black}{[BO: #1]}}
\newcommand\SH[1]{\textcolor{blue!70!gray}{[SH: #1]}}

@@

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\authorinfo{Draft}
           {}
           {}

@@

\begin{abstract}
Compositionality is a desirable characteristic for the semantics of
DSLs. In functional programming folds are used to enforce
compositionality. However folds make certain compositional
interpretations hard to express modularly. This pearl presents a
simple technique that allows non-trivial, but compositional
interpretations of DSLs to be expressed in a fully modular way
using folds.

@@

\begin{thebibliography}{}
\softraggedright

>>>>

\documentclass{jfp1}

@@

\usepackage{xcolor}
\usepackage{xspace}
%\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\graphicspath{ {images/} }

@@

\newcommand\SM[1]{\textcolor{red!70!yellow}{[SM: #1]}}
\newcommand\bruno[1]{\textcolor{green!70!black}{[BO: #1]}}
\newcommand\SH[1]{\textcolor{blue!70!gray}{[SH: #1]}}

@@

%\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
%\copyrightyear{20yy} 
%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
%\doi{nnnnnnn.nnnnnnn}

@@

%\titlebanner{banner above paper title}        % These are ignored unless
%\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\author[P. Boya and B. C. d. S. Oliveira]
        {PENG BOYA and BRUNO C. d. S. OLIVEIRA\\
         The University of Hong Kong, Hong Kong\\
         \email{bruno@cs.hku.hk}}\bruno{Fix author info later!}

%\authorinfo{Draft}
%           {}
%           {}

@@

\begin{abstract}
Compositionality is a desirable characteristic for the semantics of
DSLs. In functional programming folds can be used to enforce
compositionality. However folds make certain compositional
interpretations hard to express modularly. This pearl presents a
simple technique that allows non-trivial, but compositional
interpretations of DSLs to be expressed in a fully modular way
using folds.

@@

\begin{thebibliography}{}
%\softraggedright
